\documentclass[11pt,a4paper,sans]{moderncv}

\moderncvstyle{casual}
\moderncvcolor{blue}
%\renewcommand{\familydefault}{\sfdefault}
%\nopagenumbers{}
\usepackage[utf8]{inputenc}
%\usepackage{CJKutf8}
\usepackage[english]{babel}
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}
%\setlength{\makecvtitlenamewidth}{10cm}
% Personal data
\name{Rajat}{Sandeep Sen}
% \title{Resumé title}
\address{Thodupuzha, Kerala, India}{}{}
\phone[mobile]{+91 9846101882}
% \phone[fax]{+3~(456)~789~012}
\email{rajatsandeepsen@gmail.com}
\homepage{rajatsandeepsen.github.io}
\extrainfo{https://github.com/rajatsandeepsen}
% \photo[64pt][0.4pt]{imágen}
% \quote{Some quote}
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}

%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            Content
%----------------------------------------------------------------------------------
\begin{document}

\recipient{Sarvam AI}{Bengaluru, Karnataka, India}
\date{23-04-2026}
\opening{Greeting}
\closing{Sincerely,}
\makelettertitle

This is the second time that I'am applying to Sarvam AI. Last time i got rejected. But that didn't stop me from applying again. I have been improving myself since then and i hope this time i will get selected.

I have been following Sarvam for a long time and i know that Sarvam is the coolest place to work right now.

Recently i got the opportunity to work closely with developers from Sarvam as open source contributor. I built a package that'll improve developer experience for Sarvam API users. Officially that repository has been tranfered to Sarvam team.

I also got the chance to interact with Sarvam team and learn about the company culture. That experience has further motivated me to apply for this position.

Last year, I was studying Artificial Inteligence \& Data Science Engineering and Minor in Robotic, graduated with 8 CGPA. But Education doesn't matter anyways for this current era of AI.

But now, I'm a well experienced Full Stack Developer, DevOps and GenAI Engineer. I acquired these skills through my involements in tech communities, freelancer and while building a startup.

I have been working on various AI projects, including building GenAI tools, developing web applications, and implementing DevOps practices. My experience includes working with Python, Typescript, and various AI frameworks. I have also contributed to open-source projects and participated and won 3 hackathons, which has helped me enhance my skills and stay updated with the latest trends in AI.

I think I'm suitable for this position as 'Forward Deployed Software Engineer' at Sarvam. I would love to be a part of your team while solving interesting challenges. That'll be pretty cool to work at an AI company that's specilizes for Indian consumers. What if working from Sarvam might inspire me start my own AI company in future? I would love to be a part of that journey.

Thank you in advance for your consideration, and I look forward to hearing from you.

\makeletterclosing

\end{document}
