\documentclass[11pt,a4paper,sans]{moderncv}

\moderncvstyle{casual}
\moderncvcolor{blue}
%\renewcommand{\familydefault}{\sfdefault}
%\nopagenumbers{}
\usepackage[utf8]{inputenc}
%\usepackage{CJKutf8}
\usepackage[english]{babel}
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}
%\setlength{\makecvtitlenamewidth}{10cm}
% Personal data
\name{Rajat}{Sandeep Sen}
% \title{Resumé title}
\address{Thodupuzha, Kerala, India}{}{}
\phone[mobile]{+91 9846101882}
% \phone[fax]{+3~(456)~789~012}
\email{rajatsandeepsen@gmail.com}
\homepage{rajatsandeepsen.github.io}
\extrainfo{https://github.com/rajatsandeepsen}
% \photo[64pt][0.4pt]{imágen}
% \quote{Some quote}
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}

%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            Content
%----------------------------------------------------------------------------------
\begin{document}

\recipient{Okta}{Bengaluru, Karnataka, India}
\date{17-05-2026}
\opening{Greeting}
\closing{Sincerely,}
\makelettertitle

I am excited to apply for the Staff Software Engineer - Node.js position at Okta. With extensive experience building scalable backend systems and APIs using Node.js and TypeScript, I am confident in my ability to contribute to your platform's mission of secure identity management.

My background as a Full Stack Developer and DevOps engineer has equipped me with deep expertise in JavaScript/TypeScript ecosystems, modern tooling, and best practices for building maintainable, performant services. I have successfully built and maintained production systems handling significant scale, and I am passionate about mentoring developers and improving developer experience through thoughtful API design and robust infrastructure.

I have contributed to open-source projects and have a proven track record of collaborating with engineering teams on complex technical challenges. My experience spans building microservices, optimizing performance, and implementing DevOps practices that enable teams to move faster and more reliably.

I am particularly drawn to Okta's focus on security and identity as foundational infrastructure, and I would welcome the opportunity to bring my technical expertise and collaborative approach to your engineering team.

Thank you in advance for your consideration, and I look forward to hearing from you.

\makeletterclosing

\end{document}
